fdcoexist

### 2018-08-24 paper_simulations.Rmd
:sparkles: scenarios RA00 & RA1090 + 8% dispersal

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 8)

@@

# Competition + Dispersion coefficients
A =  0.0005	# Alpha scalar 
d = 0.00 # Dispersal percentage

@@

# Define scenarios -------------------------------------------------------------
# Scenarios on traits affecting growth and competition
trait_scenarios = list(
    RA1090   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.90, 0.10, 0),
                          compet_weight = c(0,    0.90, 0.10)),
    RA2575   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.75, 0.25, 0),
                          compet_weight = c(0,    0.75, 0.25)),
    RA5050   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.5, 0.5, 0),
                          compet_weight = c(0,   0.5, 0.5)),
    RA7525   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.25, 0.75, 0),
                          compet_weight = c(0,    0.25, 0.75)),
    RA100100 = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0, 1, 0),
                          compet_weight = c(0, 1, 0))
)

@@

trait_scenar_names = c(
    RA1090 = "Growth = 10%\nCompet. = 90%",
    RA2575 = "Growth = 25%\nCompet. = 75%",
    RA5050 = "Growth = 50%\nCompet. = 50%",
    RA7525 = "Growth = 75%\nCompet. = 25%",
    RA100100 = "Growth = 100%\nCompet. = 100%"
)

>>>>

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 9.5)

@@

# Competition + Dispersion coefficients
A =  0.0005	# Alpha scalar 
d = 0.08 # Dispersal percentage

@@

# Define scenarios -------------------------------------------------------------
# Scenarios on traits affecting growth and competition
trait_scenarios = list(
    RA00     = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(1, 0, 0),
                          compet_weight = c(0, 0, 1)),
    RA1090   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.90, 0.10, 0),
                          compet_weight = c(0,    0.90, 0.10)),
    RA2575   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.75, 0.25, 0),
                          compet_weight = c(0,    0.75, 0.25)),
    RA5050   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.5, 0.5, 0),
                          compet_weight = c(0,   0.5, 0.5)),
    RA7525   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.25, 0.75, 0),
                          compet_weight = c(0,    0.25, 0.75)),
    RA9010   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.10, 0.90, 0),
                          compet_weight = c(0,    0.10, 0.90)),
    RA100100 = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0, 1, 0),
                          compet_weight = c(0, 1, 0))
)

@@

trait_scenar_names = c(
    RA00   = "Growth = 0%\nCompet. = 0%",
    RA1090 = "Growth = 10%\nCompet. = 90%",
    RA2575 = "Growth = 25%\nCompet. = 75%",
    RA5050 = "Growth = 50%\nCompet. = 50%",
    RA7525 = "Growth = 75%\nCompet. = 25%",
    RA9010 = "Growth = 90%\nCompet. = 10%",
    RA100100 = "Growth = 100%\nCompet. = 100%"
)
